### 2015-02-22 fundamentals/impl.tex
extremes->fidelity
moved first paragraph up into IIC intro. it mentions both faciliteis and resources
clean up decay sentence

\Cyclus models facilities, institutions, regions, and resources as discrete
objects. A discrete resource model allows for a range of modeling granularity. In the
macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
microscopic extreme, the model is capable of representing arbitrarily small
material objects at isotopic resolution. In this way, \Cyclus is
applicable across the full range of modeling extremes.

Fleet-based, lumped-material models do not distinguish between discrete
facility entities or materials. However, some questions require resolution at the level of
individual facilities and materials.
As a result, many detailed performance
metrics cannot be captured with previously existing fleet-based models.

@@

For all of the reasons that the \gls{ABM} paradigm in \ref{sec:abm} enables
novel simulations, multiple use cases require that these agents, such as the
regions, institutions, and facilities in \Cyclus, must be represented as
discrete objects. Furthermore, important use cases are enabled when materials
and resources are tracked as discrete objects alongside those agents.

@@

In order to avoid excess decay calculations, when decay
is invoked, a material checks to see if it contains any nuclides with decay
constants that are significant with respect to the time change since the last
decay operation.  If none of the decay constants are significant, no decay
calculation is performed and the material remains unchanged.  This error does
not accumulate because the next time the material's decay function is invoked,
the time change will be larger.

>>>>

\Cyclus models facilities, institutions, regions, and resources as discrete
objects. A discrete resource model allows for a range of modeling granularity. In the
macroscopic extreme, it is equivalent to time-stepped continuous flow. In the
microscopic extreme, the model is capable of representing arbitrarily small
material objects at isotopic resolution. In this way, \Cyclus is
applicable across the full range of modeling fidelity.

Fleet-based, lumped-material models do not distinguish between discrete facility
entities or materials. However, some questions require resolution at the level
of individual facilities and materials.  As a result, many detailed performance
metrics cannot be captured with previously existing fleet-based models. For all
of the reasons that the \gls{ABM} paradigm in \ref{sec:abm} enables novel
simulations, multiple use cases require that these agents, such as the regions,
institutions, and facilities in \Cyclus, must be represented as discrete
objects. Furthermore, important use cases are enabled when materials and
resources are tracked as discrete objects alongside those agents.

@@

@@

When decay is invoked, A material checks to see if it contains any nuclides with
decay constants that are significant with respect to the time change since the
last decay operation.  If none of the decay constants are significant, no decay
calculation is performed and the material remains unchanged.  This error does
not accumulate because the next time the material's decay function is invoked,
the time change will be larger.
